LIME Applied to a Logistic Regression

### 2020-09-29 journals/08-logistic_regression/08-logistic_regression.Rmd
small updates

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE,
                      warning = FALSE, 
                      eval = TRUE,
                      cache = TRUE, 
                      fig.width = 12)
```

@@

```{r}
# Plot the explanation of interest
join_plots <- function(id, exp) {
  p1 <- lime::plot_features(exp$explain[id:(id+1),])
  p2 <- eoi_plot(exp$explain[id:(id+1),])
  plot_grid(p1, p2)
}
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  eval = TRUE,
  cache = FALSE,
  fig.width = 12
)
```

@@

```{r}
# Plot the explanation of interest
join_plots <- function(id, exp) {
  p1 <- lime::plot_features(exp$explain[id:(id+1),])
  p2 <- limeaid::plot_explain_scatter(exp$explain[id:(id+1),])
  plot_grid(p1, p2)
}
```
